### 2024-10-17 README.Rmd

[<img src="articles/cols4all2.jpg" width="900"/>](articles/cols4all2.jpg)

@@

[<img src="articles/cols4all_fair_sort_cbf.jpg" width="900"/>](articles/cols4all_fair_sort_cbf.jpg)

@@

[<img src="articles/cols4all_div.jpg" width="900"/>](articles/cols4all_div.jpg)

@@

[<img src="articles/c4a_pals.jpg" width="900"/>](articles/c4a_pals.jpg)

`area7`, `area8` and `area9` are fair, contain low pastel colors, and are color-blind friendly (up to 7 colors). So ideal for maps and other space-filling visualizations! These are used in [https://github.com/r-tmap/tmap](`tmap4`).

[<img src="articles/area7.jpg" width="900"/>](articles/area7.jpg)

@@

[<img src="articles/area7d.jpg" width="900"/>](articles/area7d.jpg)

@@

[<img src="articles/line7_wt.jpg" width="440"/>](articles/line7_wt.jpg)
[<img src="articles/line7_bk.jpg" width="440"/>](articles/line7_bk.jpg)

@@

[<img src="articles/friendly13.jpg" width="900"/>](articles/friendly13.jpg)

>>>>

[<img src="man/figures/cols4all2.jpg" width="900"/>](man/figures/cols4all2.jpg)

@@

[<img src="man/figures/cols4all_fair_sort_cbf.jpg" width="900"/>](man/figures/cols4all_fair_sort_cbf.jpg)

@@

[<img src="man/figures/cols4all_div.jpg" width="900"/>](man/figures/cols4all_div.jpg)

@@

[<img src="man/figures/c4a_pals.jpg" width="900"/>](man/figures/c4a_pals.jpg)

`area7`, `area8` and `area9` are fair, contain low pastel colors, and are color-blind friendly (up to 7 colors). So ideal for maps and other space-filling visualizations! These are used in [`tmap4`](https://github.com/r-tmap/tmap).

[<img src="man/figures/area7.jpg" width="900"/>](man/figures/area7.jpg)

@@

[<img src="man/figures/area7d.jpg" width="900"/>](man/figures/area7d.jpg)

@@

[<img src="man/figures/line7_wt.jpg" width="440"/>](man/figures/line7_wt.jpg)
[<img src="man/figures/line7_bk.jpg" width="440"/>](man/figures/line7_bk.jpg)

@@

[<img src="man/figures/friendly13.jpg" width="900"/>](man/figures/friendly13.jpg)
